\Russell's Metatheoretic Study - Notes

### 2006-05-31 papers/slides-ICFP'06/abstract-only.tex
Abstract sent to Christine
Spell-checked abstract and fix url

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
\usepackage{concmath}
\usepackage{url}
\usepackage{fullpage}

@@

We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.
The type system of \Russell{} is based on the
Calculus of Constructions with $\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}. We are aiming at 
a complete proof of \Russell{} metatheoretic properties (structural
properties, Subject Reduction, maybe Strong Normalization), the
refining steps which
led us to the algorithmic system and the corresponding typing algorithm and also the correctness of a
traduction from \Russell{} to the Calculus of Inductive Constructions
with metavariables.

@@

\item Subject Reduction, which is \emph{not} directly provable for the
  declarative system. Here we adapted the technique developped by
  Robin Adams \cite{adams:PTSEQ}. It includes a new term algebra, with
  associated reduction operations and a new type system
  for which we have to prove metatheoretic properties.

\item Correction of the traduction: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}

We will present these difficulties and our recipes for solving them in
the \Coq environment. Additionaly, we will identify more general problems for
proving in \Coq and suggest possible solutions.

{\bf Disclaimer}: this is a work in
progress ; to this day we have proved elimination of transivity and
subject reduction should follow soon.

>>>>

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
%\usepackage{concmath}
%\usepackage{ccfonts,eulervm}
\usepackage{concmath}
\usepackage{url} \usepackage{fullpage}

@@

We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.  The type system
of \Russell{} is based on the Calculus of Constructions with
$\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}.

We are aiming at a complete proof of \Russell{}'s metatheoretic properties
(structural properties, Subject Reduction, maybe Strong Normalization),
the refining steps which led us to the algorithmic system and the
corresponding typing algorithm and also the correctness of an interpretation
from \Russell{} to the Calculus of Inductive Constructions with
metavariables.

@@

\item Subject Reduction, which is \emph{not} directly provable for the
  declarative system. Here we adapted the technique developed by
  Robin Adams \cite{adams:PTSEQ}. It includes a new term algebra, with
  associated reduction operations and a new type system
  for which we have to prove metatheoretic properties.

\item Correction of the interpretation: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}

We will present these difficulties and our recipes for solving them in
the \Coq environment. Additionally, we will identify more general problems for
proving in \Coq and suggest possible solutions.

{\bf Disclaimer}: this is a work in
progress ; to this day we have proved elimination of transitivity and
subject reduction should follow soon.

### 2006-05-31 papers/slides-ICFP'06/notes.tex
Spell-checked abstract and fix url

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
\usepackage{amsmath}
\usepackage{concmath}
\usepackage{url}
\usepackage{fullpage}

@@

\title{\Russell's Metatheoretic Study - Notes}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  sozeau@lri.fr}
\begin{document}
\maketitle
\begin{abstract}
We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.  The type system
of \Russell{} is based on the Calculus of Constructions with
$\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}.

We are aiming at a complete proof of \Russell{} metatheoretic properties
(structural properties, Subject Reduction, maybe Strong Normalization),
the refining steps which led us to the algorithmic system and the
corresponding typing algorithm and also the correctness of a traduction
from \Russell{} to the Calculus of Inductive Constructions with
metavariables.

@@

\item Subject Reduction, which is \emph{not} directly provable for the
  declarative system. Here we adapted the technique developped by
  Robin Adams \cite{adams:PTSEQ}. It includes a new term algebra, with
  associated reduction operations and a new type system
  for which we have to prove metatheoretic properties.

\item Correction of the traduction: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}
\end{abstract}

>>>>

\documentclass{article}
\usepackage[latin1]{inputenc}
\usepackage{xspace} % To get the right spacings in front of : and so on
\usepackage[english]{babel}
\usepackage{abbrevs}
\usepackage{subfigure}
\usepackage{ifthen}
\usepackage{coqdoc}
\usepackage{bussproofs}
\usepackage{pgf,pgfarrows,pgfnodes}
\usepackage{amsmath}
%\usepackage{concmath}
\usepackage{url}
\usepackage{fullpage}

@@

\title{\Russell's Metatheoretic Study - Notes}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  sozeau@lri.fr}
\begin{document}
\maketitle
\begin{abstract}

We are working on the formalization of \Russell{}'s type theory in the
\Coq{} proof assistant \cite{sozeau:coq/Russell/meta}.  The type system
of \Russell{} is based on the Calculus of Constructions with
$\Sigma$-types (dependent sums), extended by an equivalence on types
which subsumes $\beta$-conversion. The extension permits to identify
types and subsets based on them in a manner similar to the
\emph{Predicate Subtyping} feature of \PVS{}.

We are aiming at a complete proof of \Russell{}'s metatheoretic properties
(structural properties, Subject Reduction, maybe Strong Normalization),
the refining steps which led us to the algorithmic system and the
corresponding typing algorithm and also the correctness of an interpretation
from \Russell{} to the Calculus of Inductive Constructions with
metavariables.

@@

\item Subject Reduction, which is \emph{not} directly provable for the
  declarative system. Here we adapted the technique developed by
  Robin Adams \cite{adams:PTSEQ}. It includes a new term algebra, with
  associated reduction operations and a new type system
  for which we have to prove metatheoretic properties.

\item Correction of the interpretation: the target system include
  metavariables, introducing a second, \emph{unusual} kind of variable binding.
\end{itemize}

\end{abstract}
